An Extensible Approach to Verification of Embedded Systems

### 2014-05-02 tech-project/introduction.tex

From a non-verification related perspective, a variety of tools and languages have been put forth to help make developing embedded applications a simpler, less error prone endeavor. On one end of this effort are languages such as NesC, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions. The other end of this effort is largely comprised of simulation tools such as TOSSIM, Cooja, and Avrora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments. Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed.

>>>>

From a non-verification related perspective, a variety of tools and languages have been put forth to help make developing embedded applications a simpler, less error prone endeavor. On one end of this effort are languages such as NesC\cite{Gay:2003}, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions. The other end of this effort is largely comprised of simulation tools such as TOSSIM\cite{levis:2003}, Cooja\cite{osterlind:2006}, and Avrora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments. Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed.
